\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-25 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Effet sur le papier
Revision texte papier et answer R1

Our results may be summarized in two main new findings.
First, additive transport costs are quantitatively sizable.
On average over 1974-2019, the additive cost is estimated to be \textbf{1.8\% and 2.9\% A AJUSTER} of the export price in air and vessel transport respectively (at the 3-digit classification level). This is slightly lower than our estimates for the ad-valorem component \textbf{(2.5\% and 3.2\% for air/vessel} respectively on average over the period).
Put differently, additive costs represent between \textbf{one-third and almost one-half} of the overall transport costs. To the best of our knowledge, our paper is the first to provide such an extensive quantitative measure of both ad-valorem and additive costs in total transport costs.
This represents a valuable insight for calibrating related international trade or business cycle models.
We also provide an empirical assessment of what standard international trade models lose by skipping additive transport costs.
Quantitatively, the omission of the additive term leads to overestimate the ad-valorem component by roughly a \textbf{factor~2}. Further, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the removed degree of freedom.\smallskip

Second, we find that the main source of the downward trend in overall transport costs comes mainly from the reduction of transport cost \textit{per se}, , by roughly \textbf{50\% in air shipping and 60\% in vessel shipping over 1974-2013}.\footnote{Throughout the paper, we refer to ``pure'' or ``\textit{per se}'' transport costs changes as the changes over time in the transport costs for a given product/country partner, ie excluding trade composition effects (i.e. changes over time in the baskets of imported goods and/or the origin countries).} Specifically, trade composition effects have only limited influence in accounting for the downward trend of international transport costs, and when they matter (in maritime transport), composition effects amplify the reduction of pure transport costs. This contrasts with the conclusion obtained by \cite{hummels2007} yet also on US import flows.%\footnote{Both Hummel's and our's databases come from the US Bureau of Census's import flows database, with two differences yet. First, we consider a larger period of time, spanning from 1974 (as in \cite{hummels2007}) to 2019 (while he stops in 2004). Second, while Hummels considers products at the 5-digit classification level, we are able to exploit heterogeneity in the data at the much more disaggregated HS-10 level for the vast majority of the period (1989-2019). For the period 1974-1988, we rely on Hummel's original database with a 5-digit product classification level.}
\cite{hummels2007} finds that total transport costs have decreased in both air and maritime shipment, but less so than ``pure'' transport costs, because trade composition effects have partly offset the pure transport costs decrease, thereby attenuating the overall downward trend in transport costs. Importantly, we show that the difference of results can be attributed to the new method of modeling the additive component that we offer. Allowing the share of additive costs to vary across time, products and country partners (rather than being constant as in \citealp{hummels2007}), turn out to be key in the decomposition of underlying sources of the decrease of overall transport costs observed over the period.

\smallskip
In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
In this respect, it contributes to the literature that challenges the dominant role of iceberg costs in international trade (even in the case of ice transport, see \citealp{bosker2018ice}). As shown by \cite{alchian}, the relative price of two varieties of some goods will depend on the level of additive trade costs. In this context, the relative demand for more expensive/higher-quality product goods increases with trade costs (``shipping the good apples out''). This is consistent with the empirical findings by \cite{hummels_skiba}, who estimate the elasticity of freight rates with respect to price to be well below unity.\footnote{Also, their estimates imply that doubling freight costs increases average free alongside ship (fas) export prices by 80\% to 141\%, consistent with high-quality goods being sold in markets with high freight costs.}
Recent empirical studies based on micro-level data also provide strong empirical support for the role of additive costs (i.e. cost per unit exported) in international trade costs.\footnote{Based on a firm-product-level database of French exporters, \cite{martin2012} finds that firms charge higher unit values for exports to more remote countries, supporting the importance of additive costs.
Using transaction-level trade data from Colombia, \cite{Lashkaripour-2018} estimates that the transport cost elasticity varies greatly across industries, with a value of 0.8 for the average industry, in contrast with the iceberg specification.} If in empirical support for additive trade costs, these papers yet do not allow for a quantitative measure of these cost (neither for the ad-valorem costs). One important contribution of the paper is to provide quantitative estimates of both type of transport costs.\footnote{On top of the previously cited papers about additive costs, our paper also relates to \cite{Kropf-Saure-JIE-2016}, who estimate the size and shape of per-shipment costs based on Swiss data, and to \cite{Alessandria-et-al-AER-2010} or \cite{Hornok-et-al-JIE-2015, Hornok-et-al-RES-2015}, who point out the role of per-shipment costs (among which, administrative costs) in generating some ``lumpiness'' in international trade transactions.} \smallskip

Closely related to our paper is the work by \cite{Irrazabal_2015}, which develops a structural framework for inferring relative additive trade costs from firm-level trade data.
Implementing their methodology on Norwegian firm-level export data for the year 2004, they find that, for the median shipment, additive costs (in Norwegian crowns) amount to 6\% of the export price multiplied by the ad-valorem cost (also expressed in Norwegian crowns).
Our results share in common with \cite{Irrazabal_2015} the important role of the additive component of international trade costs.
Yet, our paper complements their findings in two main respects.
First, while our study covers a narrower set of trade costs focused on transport costs, their data and their empirical approach only allows the identification of the ratio of the additive cost to the export price multiplied by the ad-valorem cost; by contrast, our estimation strategy enables us to uncover separately both values of the ad-valorem and the additive costs.
From this, we can rebuild the ratio in similar terms to them, thereby gaining in generality in this respect.
While \cite{Irrazabal_2015} find that, for an export price multiplied by the ad-valorem cost of 100 USD, 6 USD are paid in additive trade costs, our results point to a value paid in additive transport costs of \textbf{2.8 USD for maritime shipping and 1.5 USD for air transport for 2004.}
This comparison of results suggests that between \textbf{a third and a half of the additive trade costs} are attributable to the transport sector (depending on the transport mode).
Second, we exploit exhaustive information about the imports flows of the US over a wide time-span from 1974 to 2019.
In this respect, our results deliver a broader view of the magnitude of additive costs in international trade over time.
In particular, we show that the modeling of additive costs is of critical importance in determining the underlying sources of the trends patterns of international transport costs observed over the last fifty years.

\textbf{Big Picture}.
Our results have important implications for both international trade and international macroeconomics models. Beyond the positive aspect, several recent papers also point out the normative implications of additive trade costs.\footnote{ \cite{sorensen2014} extends \cite{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}} These results suggest that important welfare gains can be achieved by reducing additive trade costs. On the same toke, as additive costs distort relative prices, they are very likely to affect the international transmission of shocks in international business cycles models. In both fields yet, not much progress has been made in quantifying such gains. One potential reason is the lack of an empirical characterization of the additive component of trade costs (the one exception being \citealp{Irrazabal_2015}). The quantitative results we provide in the paper allow making one step in filling that gap. \textbf{To develop}. \medskip

The paper is built as follows.
First, we estimate the values of international transport costs annually throughout the period 1974-2013 by transport mode, explicitly distinguishing between the additive and the ad-valorem components.
 Section \ref{sec:data_method} reports the mean values of the transport costs estimated over the period (by transport mode).
Relying on these estimation results, we then provide a decomposition of the transport costs trend patterns, between what arises from changes in the trade composition (by product and/or partner country), and what is attributable to changes in transport costs \textit{per se}.
Section \ref{sec:results_trends} is devoted to this analysis, while Section \ref{sec:robustness} checks the robustness of our results to the separability assumption and the weighting scheme.
Section \ref{sec:conclu} concludes.

@@

\section{The role of additive cost: Theoretical insights}

@@

$f$ such that all firms produce in autarky (i.e., such that $\varphi^{\ast,a} = \varphi_{\text{min}}$. $f_x$ endogenously revealed such that the initial steady state (with 1974 values of transport costs) implies a share of exporting firms equal to 21\%, based on \textbf{???}, following so the calibration method of \cite{ghironi} or \cite{Irrazabal_2015}.

@@

Second, we take into account the fact that the share of exporting firms has substantially increased since the 21\% value estimated by \textbf{???} in \textbf{YEAR YYY}. According to \textbf{???}, this share roughly amounts to 35\% in \textbf{???}. This can be matched in the model by resetting the (lower) value of the export fixed cost $f_x$ accordingly. In the second exercise, we thus run a comparative statics analysis where we contrast the 2014 steady states (e.g., with the 2019 transport costs values) with the two dimensions of trade liberalization: the reduction of transport costs (as in the first exercise) and the reduction of the export fixed cost, consistent with the increase in the share of exporters from 21\% to 35\%.

The results are reported in Table \ref{tab:resultats_modele}, for Air (Columns (1)-(4)) and Vessel (Columns (5)-(8)) respectively. Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms.
For each transport mode, the first two columns report the results of reducing transport costs only, maintaining the same value of $f_x$ as in the initial equilibrium (Columns (A)-(B) for Air, (E)-(F) for Vessel), contrasting the case of only ad-valorem costs (Columns (A), (D)) and in presence of additive costs (Columns (B), (F)). Columns (C)-(D) for Air and (G)-(H) for Vessel report the results when both the variable transport costs and the fixed export costs are lower in the final steady state (2019) relative to the initial one (1974).

>>>>

Our results may be summarized in two main new findings.
First, additive transport costs are quantitatively sizable.
On average over 1974-2019, the additive cost is estimated to be 1.7\% and 2.8\% of the export price in air and vessel transport respectively (at the 3-digit classification level). This is slightly lower than our estimates for the ad-valorem component (2.4\% and 3\% for air/vessel respectively on average over the period).
Put differently, additive costs represent on average between 30 and 45\% of the overall transport costs. To the best of our knowledge, our paper is the first to provide such an extensive quantitative measure of both ad-valorem and additive costs in total transport costs.
This represents a valuable insight for calibrating related international trade or business cycle models.
We also provide an empirical assessment of what standard international trade models lose by skipping additive transport costs.
Quantitatively, the omission of the additive term leads to overestimate the ad-valorem component by a factor ranging between 1.5 and 1.8. Further, the goodness of fit is systematically better when the additive component is included in the regression, even when taking into account the removed degree of freedom.\smallskip

Second, we find that the main source of the downward trend in overall transport costs comes mainly from the reduction of transport cost \textit{per se}, , by roughly \textbf{50\% in air shipping and 60\% in vessel shipping over 1974-2019}.\footnote{Throughout the paper, we refer to ``pure'' or ``\textit{per se}'' transport costs changes as the changes over time in the transport costs for a given product/country partner, ie excluding trade composition effects (i.e. changes over time in the baskets of imported goods and/or the origin countries).} Specifically, trade composition effects have only limited influence in accounting for the downward trend of international transport costs, and when they matter (in maritime transport), composition effects amplify the reduction of pure transport costs. This contrasts with the conclusion obtained by \cite{hummels2007} yet also on US import flows.%\footnote{Both Hummel's and our's databases come from the US Bureau of Census's import flows database, with two differences yet. First, we consider a larger period of time, spanning from 1974 (as in \cite{hummels2007}) to 2019 (while he stops in 2004). Second, while Hummels considers products at the 5-digit classification level, we are able to exploit heterogeneity in the data at the much more disaggregated HS-10 level for the vast majority of the period (1989-2019). For the period 1974-1988, we rely on Hummel's original database with a 5-digit product classification level.}
\cite{hummels2007} finds that total transport costs have decreased in both air and maritime shipment, but less so than ``pure'' transport costs, because trade composition effects have partly offset the pure transport costs decrease, thereby attenuating the overall downward trend in transport costs. Importantly, we show that the difference of results can be attributed to the new method of modeling the additive component that we offer. Allowing the share of additive costs to vary across time, products and country partners (rather than being constant as in \citealp{hummels2007}), turn out to be key in the decomposition of underlying sources of the decrease of overall transport costs observed over the period.

\smallskip
In both aspects, our results point to the importance of the additive component in accounting for international transport costs.
In this respect, it contributes to the literature that challenges the dominant role of iceberg costs in international trade (even in the case of ice transport, see \citealp{bosker2018ice}). As shown by \cite{alchian}, the relative price of two varieties of some goods will depend on the level of additive trade costs. In this context, the relative demand for more expensive/higher-quality product goods increases with trade costs (``shipping the good apples out''). This is consistent with the empirical findings by \cite{hummels_skiba}, who estimate the elasticity of freight rates with respect to price to be well below unity.\footnote{Also, their estimates imply that doubling freight costs increases average free alongside ship (fas) export prices by 80\% to 141\%, consistent with high-quality goods being sold in markets with high freight costs.}
Recent empirical studies based on micro-level data also provide strong empirical support for the role of additive costs (i.e. cost per unit exported) in international trade costs.\footnote{Based on a firm-product-level database of French exporters, \cite{martin2012} finds that firms charge higher unit values for exports to more remote countries, supporting the importance of additive costs.
Using transaction-level trade data from Colombia, \cite{Lashkaripour-2017} estimates that the transport cost elasticity varies greatly across industries, with a value of 0.8 for the average industry, in contrast with the iceberg specification.} If in empirical support for additive trade costs, these papers yet do not allow for a quantitative measure of these cost (neither for the ad-valorem costs). One important contribution of the paper is to provide quantitative estimates of both type of transport costs.\footnote{On top of the previously cited papers about additive costs, our paper also relates to \cite{Kropf-Saure-JIE-2016}, who estimate the size and shape of per-shipment costs based on Swiss data, and to \cite{Alessandria-et-al-AER-2010} or \cite{Hornok-et-al-JIE-2015, Hornok-et-al-RES-2015}, who point out the role of per-shipment costs (among which, administrative costs) in generating some ``lumpiness'' in international trade transactions.} \smallskip

Closely related to our paper is the work by \cite{Irrazabal_2015}, which develops a structural framework for inferring relative additive trade costs from firm-level trade data.
Implementing their methodology on Norwegian firm-level export data for the year 2004, they find that, for the median shipment, additive costs (in Norwegian crowns) amount to 6\% of the export price multiplied by the ad-valorem cost (also expressed in Norwegian crowns).
Our results share in common with \cite{Irrazabal_2015} the important role of the additive component of international trade costs.
Yet, our paper complements their findings in two main respects.
First, while our study covers a narrower set of trade costs focused on transport costs, their data and their empirical approach only allows the identification of the ratio of the additive cost to the export price multiplied by the ad-valorem cost; by contrast, our estimation strategy enables us to uncover separately both values of the ad-valorem and the additive costs.
From this, we can rebuild the ratio in similar terms to them, thereby gaining in generality in this respect.
While \cite{Irrazabal_2015} find that, for an export price multiplied by the ad-valorem cost of 100 USD, 6 USD are paid in additive trade costs, our results point to a value paid in additive transport costs of 2.8 USD for maritime shipping and 1.5 USD for air transport for 2004.
This comparison of results suggests that between a quarter and a half of the additive trade costs are attributable to the transport sector (depending on the transport mode).%JH : these results should not change, they are for 2004. 
Second, we exploit exhaustive information about the imports flows of the US over a wide time-span from 1974 to 2019.
In this respect, our results deliver a broader view of the magnitude of additive costs in international trade over time.
In particular, we show that the modeling of additive costs is of critical importance in determining the underlying sources of the trends patterns of international transport costs observed over the last fifty years.

%\textbf{Big Picture}.
Our results are robust to a range of robustness check, including different weighting schemes, the use of instrumental variables and more disaggregated data at the HS10 level. They have important implications for both international trade and international macroeconomics models. Beyond the positive aspect, several recent papers also point out the normative implications of additive trade costs.\footnote{ \cite{sorensen2014} extends \cite{melitz}'s seminal model of international trade by including additive trade costs, in addition to the ad-valorem component. A key analytical result is that the welfare gain from a reduction in trade barriers is higher for a decrease in additive costs than a decrease in ad-valorem costs, due to the alteration of relative prices in a heterogeneous-firms trade framework. This is confirmed by \cite{Irrazabal_2015}} These results suggest that important welfare gains can be achieved by reducing additive trade costs. On the same toke, as additive costs distort relative prices, they are very likely to affect the international transmission of shocks in international business cycles models. In both fields yet, not much progress has been made in quantifying such gains. One potential reason is the lack of an empirical characterization of the additive component of trade costs (the one exception being \citealp{Irrazabal_2015}). The quantitative results we provide in the paper allow making one step in filling that gap.

More precisely, we use our estimates of multiplicative and additive costs for the years 1974 and 2019 to implement several comparative static exercises investigating the different welfare consequences of alterations to multiplicative and additive costs. For a given decrease in transport costs, welfare gains are around 50\% higher when the underlying framework allows for additive costs - which, in practice, concentrate the major part of transport costs decrease over the period. In addition, we also assess how the latter results are distorted by changes in sunk costs of exports (i.e., increase in the share of exporting firms). Welfare gains are proportionally amplified, with again an additional premium coming from the decrease of additive costs.

%\textbf{To develop}. \medskip

The remainder of the paper is built as follows. First, we estimate the values of international transport costs annually throughout the period 1974-2013 by transport mode, explicitly distinguishing between the additive and the ad-valorem components. Section \ref{sec:data_method} reports the mean values of the transport costs estimated over the period (by transport mode). Relying on these estimation results, we then provide a decomposition of the transport costs trend patterns, between what arises from changes in the trade composition (by product and/or partner country), and what is attributable to changes in transport costs \textit{per se}. Section \ref{sec:results_trends} is devoted to this analysis, while Section \ref{sec:robustness} provides several important robustness checks of our results. Section\ref{sec:theory} implements several theory-based calibration exercises to investigate the different welfare consequences of alterations to multiplicative and additive costs., and section \ref{sec:conclu} concludes.

@@

\section{The role of additive cost: Theoretical insights}\label{sec:theory}

@@

$f$ such that all firms produce in autarky (i.e., such that $\varphi^{\ast,a} = \varphi_{\text{min}}$. $f_x$ endogenously revealed such that the initial steady state (with 1974 values of transport costs) implies a share of exporting firms equal to 21\%\footnote{Though we could not find exact numbers for the share of exporting firms in 1974, this value of 21\% seems reasonable considering values reported for the 1980s by \citet{Lincoln_McCallum2018}} following so the calibration method of \cite{ghironi} or \cite{Irrazabal_2015}.

@@

Second, we take into account the fact that the share of exporting firms has substantially increased since the 21\% value reported by \citet{Lincoln_McCallum2018} for 1987. According to \textbf{???}, this share roughly amounts to 35\% in \textbf{???}. This can be matched in the model by resetting the (lower) value of the export fixed cost $f_x$ accordingly. In the second exercise, we thus run a comparative statics analysis where we contrast the 2014 steady states (e.g., with the 2019 transport costs values) with the two dimensions of trade liberalization: the reduction of transport costs (as in the first exercise) and the reduction of the export fixed cost, consistent with the increase in the share of exporters from 21\% to 35\%.

The results are reported in Table \ref{tab:resultats_modele}, for Air (Columns (A)-(D)) and Vessel (Columns (E)-(H)) respectively. Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms.
For each transport mode, the first two columns report the results of reducing transport costs only, maintaining the same value of $f_x$ as in the initial equilibrium (Columns (A)-(B) for Air, (E)-(F) for Vessel), contrasting the case of only ad-valorem costs (Columns (A), (D)) and in presence of additive costs (Columns (B), (F)). Columns (C)-(D) for Air and (G)-(H) for Vessel report the results when both the variable transport costs and the fixed export costs are lower in the final steady state (2019) relative to the initial one (1974).
